On the minimum leaf conductance

### 2017-08-23 figures.Rmd
Update figures Rmd; captions written; more references

---
title: "gmin figures"
author: "Remko Duursma"
date: "1 August 2017"
output: 
  html_document:
    theme: flatly
---

```{r}
source("R/load.R")
pacman::p_load(magicaxis)
```

```{r}
v <- gmindat$gmin
hist(v, breaks=30, xlim=c(0,40), main="", freq=FALSE,
     ylim=c(0,0.15),
     col="lightgrey",
     xlab=expression(g[min]~~(mmol~m^-2~s^-1)))
curve(dlnorm(x, mean(log(v)), sd=sd(log(v))), add=TRUE,
      n=501)
```

```{r}
v <- log10(gmindat$gmin)
par(yaxs="i", mgp=c(3,1,0), cex.lab=1.2)
hist(v, breaks=30, main="", freq=FALSE,
     #ylim=c(0,0.15),
     xlim=c(-1,2),
     col="lightgrey",
     axes=FALSE,
     xlab=expression(g[min]~~(mmol~m^-2~s^-1)))
magaxis(side=1, unlog=1, usepar=TRUE)
axis(2)
curve(dnorm(x, mean=mean(v), sd=sd(v)), add=TRUE,
      n=101)

```

```{r, fig.cap="Figure 1.", fig.width=6, fig.height=6}
figure_sim()
```

@@

@@

```{r, fig.width=3, fig.height=4}
figure_gmin_bygroup(gmindat)
```

@@

@@

```{r, fig.width=6, fig.height=5}
gmin_by_family(gmindat)
```

```{r, fig.width=6, fig.height=5}
gmin_by_order(gmindat)
```

>>>>

---
title: "On the minimum leaf conductance"
author: ""
date: "1 August 2017"
output: 
  html_document:
    theme: flatly
csl: global-change-biology.csl
bibliography: references.bib
---

```{r, echo=FALSE}
source("R/load.R")
pacman::p_load(magicaxis)
knitr::opts_chunk$set(warning = FALSE, echo=FALSE)
```

```{r, fig.width=6, fig.height=6}
figure_sim()
```

**Figure 1**. Simulations  of intrinsic water-use efficiency (A~n~/g~s~), intercellular CO~2~ concentration (C~i~) and leaf transpiration rate (E~L~) with three values of g~0~. For the top two panels, all environmental drivers were held constant except the photosynthetic photon flux density (PPFD), demonstrating that the inclusion of g~0~ is necessary to simulate the decrease in A~n~/g~s~ at low PPFD. For the bottom two panels, VPD and T~air~ were covaried based on an empirical relationship [@duursma2014], reflecting typical covariation in field conditions. For all simulations it is assumed that T~leaf~ is equal to T~air~.

```{r, fig.width=8, fig.height=4}
figure_g0g1_cor(lin2015, "Nicolas Martin-StPaul_Quercus ilex_StPaul_Puechabon")
```

**Figure 2**. Example linear regression of stomatal conductance (g~s~) against a stomatal index, in this case the linearized version of the model of Medlyn et al. (2011). This example shows a very good fit between g~s~ and the stomatal index, and was selected from the database of Lin et al. (2015). The solid line is regression line, and the shaded area a 95% confidence interval for the mean. The right panel visualizes the correlation between estimated slope (g~1~) and intercept (g~0~) of the regression. The dotted ellipse is a bivariate 95% confidence interval for slope and intercept. The symbols represent 1000 bootstrap samples of the coefficients.

@@

**Figure 3**. Estimates of g~0~ depend on the overall goodness of fit. In the left panel, we fitted the linearized form of the Medlyn et al. (2011) model to each of the datasets in the Lin et al. (2015) database. Vertical lines are 95% confidence intervals. In the middle panel, a very similar association between g~0~ and R^2^ is presented by the review of @miner2017, using the Ball-Berry model. In the right panel, shown is the correlation between the standard error of the estimate of g~0~ and the coefficient of variation of the Ball-Berry coefficient (A/Ca*sqrt(D)), showing that good estimates of g~0~ can only be obtained when there is much variation in the drivers.

@@

**Figure 4**. Comparison of various estimates of the minimum conductance. Error bars are 95\% confidence intervals. Different letters denote significant differences (at $\alpha$ = 0.05). See Table 1 for definitions of minimum conductance, and text for the data sources. g~cut,isol~, cuticular permeance on isolated cuticles, g~cut,seal~, mass loss of detached leaves when stomatal side of the leaf is sealed (*might remove this*), g~min~ minimum conductance with mass loss of detached leaves, g~dark~ nighttime conductance (from Lombardozzi), g~0~ fitted parameter, using the Lin database and Miner 2017, g~s,lowA~ stomatal conductance from the Lin database, calculated for each study where A~n~ < 2.

```{r, fig.height=3, fig.with=8}
gmin_3panel(gmindat, cropgmin)
```

**Figure 5**. Literature compilation of minimum conductance (g~min~), measured with mass loss of detached leaves. Left panel, distribution across all 220 species values extracted from the literature, showing a log-normal distribution. Mean=, sd=. Middle panel, g~min~ shown by taxonomic order. Note higher g~min~ for grasses (Poales), but otherwise few clear differences. Sample size (number of species) shown on top of the figure. Right panel: genotypic variation in g~min~ for 9 major crops. Sample sizes are the number of distinct crop genotypes on which g~min~ was reported for each crop, bars denote the range in g~min~ across all the data for a crop, illustrating the very large genotypic variation compared to inter-specific variation.

@@

**Figure 6**. Minimum conductance measured from leaf dry-down curves on *Eucalyptus parramattensis* grown in whole-tree chambers. Trees were grown following ambient conditions, or in a constant elevated temperature treatment (+3 degrees C). Measurements of g~min~ were carried out at five different temperatures on replicate leaves. There is no effect of measurement T on g~min~, but leaves of trees grown in elevated temperature showed consistently lower g~min~.

@@

**Figure 7**. Minimum conductance measured from leaf dry-down curves on a variety *Hakea* species, a genus native to Australia. Plants were grown in containers in a grow house, and supplied with ample water or underwent long-term mild drought stress. Bars are labelled by leaf form : broadleaf (B) or needle-like (N). For droughted plants, g~min~ was higher for species with needle-like leaves (Wilcoxon test, p `r pval(wilcox.test(gmin.d ~ leaf.form, data=lopw)$p.value)`)), but not for well-watered plants (p `r pval(wilcox.test(gmin.w ~ leaf.form, data=lopw)$p.value)`).

# References

### 2017-08-23 manuscript.Rmd
Update figures Rmd; captions written; more references

plotfig <- function(...)grid.raster(readPNG(...))

source("R/load.R")

pval <- function(...)formatPval(..., includeEquality=TRUE)
```

@@

\
Stomata exert a strong control on the transpiration rate of leaves. It is well known that stomata respond quickly to changes in light intensity, humidity and CO~2~ concentration at the leaf surface. In doing so, stomata can be thought to balance the uptake of CO~2~ with the loss of water, and thus can be expected to close stomata when photosynthetic rates are low. To avoid desiccation and ultimate death, stomata can also be expected to close during periods of severe water stress. Plants cannot, however, completely halt water loss even when stomata are closed. In this review, we discuss various aspects of the minimum leaf conductance reached when stomata are essentially closed. We pay special attention to the role that minimum conductance plays in land-surface models, in particular as it forms part of the much-used 'Ball-Berry'-type class of stomatal conductance models.

\
Most current-generation process-baed global vegetation models (GVMs) use a version of the Ball-Berry class of stomatal conductance (g~s~) models characterized by the dependence on assimilation rate, CO~2~ and humidity.

@@

Although we use the term cuticular conductance freely, this transport pathway does not represent a true conductance since water does not diffuse as a gas through the cuticle. Instead, it dissolves into the medium of the cuticle, diffuses through the solid matrix, and is desorped at the outer edge of the cuticle [@kerstiens1996; @riederer2001; @schreiber1996]. The main barrier to diffusion is actually a very thin layer at the leaf surface. Because most of the resistance is located in such a thin layer, g~cut~ does not correlate with the thickness of the cuticle  [@priestley1943; @riederer2001; @anfodillo2002; @schuster2016b]. Nonetheless there is considerable variation in cuticle thickness between plant species [@schuster2016a], as well as within species in response to drought (cite), along altitudinal transects [@delucia1984], and even with increasing height in the canopy of very tall trees [@woordruff2010]. If the cuticle thickness does not directly affect its conductance, what is the value of increasing the cuticle? Perhaps the answer lies in mechanical strength rather than water loss per se, as @onoda2012 reported that thicker cuticles are more resistant to tearing (the force to tear and tensile strength both approx proportional to cuticle thickness).

@@

@@

>>>>

source("R/load.R")
```

# Abstract

@@

\
Stomata exert a strong control on the transpiration rate of leaves [@bange1953]. It is well known that stomata respond quickly to changes in light intensity, humidity and CO~2~ concentration at the leaf surface. In doing so, stomata can be thought to balance the uptake of CO~2~ with the loss of water, and thus can be expected to close stomata when photosynthetic rates are low. To avoid desiccation and ultimate death, stomata can also be expected to close during periods of severe water stress. Plants cannot, however, completely halt water loss even when stomata are closed. In this review, we discuss various aspects of the minimum leaf conductance reached when stomata are essentially closed. We pay special attention to the role that minimum conductance plays in land-surface models, in particular as it forms part of the much-used 'Ball-Berry'-type class of stomatal conductance models.

\
Most current-generation process-based global vegetation models (GVMs) use a version of the Ball-Berry class of stomatal conductance (g~s~) models characterized by the dependence on assimilation rate, CO~2~ and humidity.

@@

Although we use the term cuticular conductance freely, this transport pathway does not represent a true conductance since water does not diffuse as a gas through the cuticle. Instead, it dissolves into the medium of the cuticle, diffuses through the solid matrix, and is desorped at the outer edge of the cuticle [@kerstiens1996; @riederer2001; @schreiber1996]. The main barrier to diffusion is actually a very thin layer at the leaf surface. Because most of the resistance is located in such a thin layer, g~cut~ does not correlate with the thickness of the cuticle  [@priestley1943; @riederer2001; @anfodillo2002; @schuster2016b]. Nonetheless there is considerable variation in cuticle thickness between plant species [@schuster2016a], as well as within species in response to drought (cite), along altitudinal transects [@delucia1984], and even with increasing height in the canopy of very tall trees [@woordruff2010]. If the cuticle thickness does not directly affect its conductance, what is the value of increasing the cuticle?

Perhaps the answer lies in mechanical strength rather than water loss per se, as @onoda2012 reported that thicker cuticles are more resistant to tearing (the force to tear and tensile strength both approx proportional to cuticle thickness). Providing support for the mechanical strength rather than water loss idea, thick cuticles may be useful because  exposure to wind has been shown to dislodge cuticular compounds by absrasion [@rogge1993], thereby dramatically increasing the conductance of the cuticle [@hadley1983;@grace1974;@vangardingen1991]. Similarly, exposure to simulated rain damages the cuticle and increases its conductance [@baker1986].

It is also important to bear in mind other functions of the cuticle, particularly as a barrier for fungal pathogens, and insect herbivory [@kerstiens1996c].

@@

@bengtson1978 lower g~min~ in six oat varieties, and increase in cuticular waxes, but no overall relationship between the two and very different responses between different oat genotypes.

@@

@paje1988 lower gmin in droughted soybean genotypes

@saneoka1987 lower g~min~ (but different technique!) in three crop species exposed to low soil water conditions for a month.
